\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-03-15 manuscript/manuscript.tex
paper compiles now

The Kolmogorov-Smirnov (KS) statistic is widely used to test if a sample is
from a given distribution. This study demonstrates how non-parametric 
block bootstrap can be 
used to approximate the KS statistic in situations where parameters are 
not specified and the data are serially dependent. We demonstrate the 
theoretical justication for this method, then through simulation we verify that
it holds it size under the null distribution and is powerful when the null 
hypothesis is false. Finally, we demonstrate applications of the method to
the S&P 100 and S&P 500 indices stock returns.

@@

The remainder of this paper is structured as follows: 
Section~\ref{sec:methods} provides an overview of the block bootstrap 
procedure and introduces the bias correction methodology for the 
non-parametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
into two parts; initially, we evaluate the KS test's ability to maintain 
its size, i.e., its consistency in not rejecting the null hypothesis when 
it is indeed true. Subsequently, we examine the test's power, assessing 
whether it can reject the null hypothesis when it is false. Practical 
applications of our method are presented in Section~\ref{sec:real}, where 
we apply the approach to analyze if S&P 100 and S&P 500 index stock return data adhere to either the Normal 
or the Student's $t$ distribution in Subsection~\ref{sec:sp100} and
\ref{sec:sp500}. The 
paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
and remarks.

@@

Using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the SP500 index. We
observed how the method performs using increasingly smaller durations of
time.
We used the last 5 years of data: January 1st, 2019 to December 31st, 2023,
4 years of data: January 1st, 2020 to December 31st, 2023,
3 years of data: January 1st, 2021 to December 31st, 2023,
2 years of data: January 1st, 2022 to December 31st, 2023,
and 1 year of data: January 1st, 2023
to December 31st, 2023.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP5001}--\ref{table:SP5005}.

@@

Once again using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the SP100 index. We varied the
durations as we did with the SP500 index.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP1001}--\ref{table:SP1005}.
For a duration of 4 years, our method fails to reject that
the series follows the $v = 5$ Student's $t$ distribution with p-value .092,
wheraeas \citep{babu2004goodness}'s method finds a p-value of .031, and 
\citet{zeimbekakis2022misuses}'s method finds a p-value of .027.

>>>>

The Kolmogorov-Smirnov (KS) statistic is widely used to test if a sample is
from a given distribution. This study demonstrates how non-parametric 
block bootstrap can be 
used to approximate the KS statistic in situations where parameters are 
not specified and the data are serially dependent. We demonstrate the 
theoretical justication for this method, then through simulation we verify that
it holds it size under the null distribution and is powerful when the null 
hypothesis is false. Finally, we demonstrate applications of the method to
the S\&P 100 and S\&P 500 indices stock returns.

@@

The remainder of this paper is structured as follows: 
Section~\ref{sec:methods} provides an overview of the block bootstrap 
procedure and introduces the bias correction methodology for the 
non-parametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
into two parts; initially, we evaluate the KS test's ability to maintain 
its size, i.e., its consistency in not rejecting the null hypothesis when 
it is indeed true. Subsequently, we examine the test's power, assessing 
whether it can reject the null hypothesis when it is false. Practical 
applications of our method are presented in Section~\ref{sec:real}, where 
we apply the approach to analyze if S\&P 100 and S\&P 500 index stock return data adhere to either the Normal 
or the Student's $t$ distribution in Subsection~\ref{sec:sp100} and
\ref{sec:sp500}. The 
paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
and remarks.

@@

Using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the S\&P 500 index. We
observed how the method performs using increasingly smaller durations of
time.
We used the last 5 years of data: January 1st, 2019 to December 31st, 2023,
4 years of data: January 1st, 2020 to December 31st, 2023,
3 years of data: January 1st, 2021 to December 31st, 2023,
2 years of data: January 1st, 2022 to December 31st, 2023,
and 1 year of data: January 1st, 2023
to December 31st, 2023.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP5001}--\ref{table:SP5005}.

@@

Once again using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices for the S\&P 100 index. We varied the
durations as we did with the S\&P 500 index.
We approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
The p-values for these tests are highlighted in 
Tables~\ref{table:SP1001}--\ref{table:SP1005}.
For a duration of 4 years, our method fails to reject that
the series follows the $v = 5$ Student's $t$ distribution with p-value .092,
wheraeas \citep{babu2004goodness}'s method finds a p-value of .031, and 
\citet{zeimbekakis2022misuses}'s method finds a p-value of .027.
